AIR4Children: Artificial Intelligence and Robotics for Children

### 2021-02-21 article/tex/main.tex
create a new branch; and amends mathematical thinking to computational thinking

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
In this work, we proposed AIR4Children, artificial intelligence for children, as a way to (a) tackle aspects for inclusion, accessibility, transparency, equity, fairness and participation and (b) to create affordable child-centred materials in AI and robotics.
We present current challenges and opportunities for a child-centred approaches for AI and robotics (AIR). 
Similarly, we touch on open-sourced software and hardware technologies to make a more inclusive, transparent and fair participation of children in areas of AIR. 
Then, we describe the avenues that AIR4Children can take with the development of open-sourced software and hardware.
Similarly, we propose to follow the philosophy of Montessori education 
to help children to not only develop mathematical thinking but also to internalise new concepts and learning skills through activities of movement and repetition with open source robots.
Finally, we add conclusions and mainly we pose the future work to go of AIR4children to putting in practice what is proposed here and measure the impact on AI and robotics of children. 
\end{abstract}

@@

\subsection{Open teaching materials}
Considering teaching materials of AI and Robotics to be child-like oriented, AIR4Children is then adopting Montessori's education with philosophy orbited around the quote “the hand is the instrument of the mind.” \cite{montessori2013absorbent}.
In that way, materials for AIR4Children are based on Montessori education with the aim to help children to internalise new concepts and to develop concentration of their learning skills through activities of movement and repetition.
%For instance, the best way a child can concentrate is by fixing his attention on some task he is performing with his hands. 
One potential way to develop such skills is by designing activities in AI and robotics that are appropriately introduced in development stages \cite{bers2008, bers-horn2010, kazakoff-bers2012} as well as the development of grasping and understanding mathematical concepts (e.g. numbers, size, and shapes) \cite{bers2012, resnick1998}.
Similarly, as Elkin et al. (2014) \cite{elkin2014} explained, air4children can provide a way to engage children in problem-solving activities based on Montessori education as well as design activities that allow children to participate in creative explorations, develop fine motor skills, hand-eye coordination, engage in collaborative and teamwork activities.

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
In this work, we proposed AIR4Children, artificial intelligence for children, as a way to (a) tackle aspects for inclusion, accessibility, transparency, equity, fairness and participation and (b) to create affordable child-centred materials in AI and robotics.
We present current challenges and opportunities for a child-centred approaches for AI and robotics (AIR). 
Similarly, we touch on open-sourced software and hardware technologies to make a more inclusive, transparent and fair participation of children in areas of AIR. 
Then, we describe the avenues that AIR4Children can take with the development of open-sourced software and hardware.
Similarly, we propose to follow the philosophy of Montessori education 
to help children to not only develop computational thinking but also to internalise new concepts and learning skills through activities of movement and repetition with open source robots.
Finally, we add conclusions and mainly we pose the future work to go of AIR4children to putting in practice what is proposed here and measure the impact on AI and robotics of children. 
\end{abstract}

@@

\subsection{Open teaching materials}
Considering teaching materials of AI and Robotics to be child-like oriented, AIR4Children is then adopting Montessori's education with philosophy orbited around the quote “the hand is the instrument of the mind.” \cite{montessori2013absorbent}.
In that way, materials for AIR4Children are based on Montessori education with the aim to help children to internalise new concepts and to develop concentration of their learning skills through activities of movement and repetition.
%For instance, the best way a child can concentrate is by fixing his attention on some task he is performing with his hands. 
One potential way to develop such skills is by designing activities in AI and robotics that are appropriately introduced in development stages \cite{bers2008, bers-horn2010, kazakoff-bers2012} as well as the development of grasping and understanding mathematical concepts (e.g. numbers, size, and shapes) and computational thinking (e.g. variables, loops, counters, etc) \cite{bers2012, resnick1998}.
Similarly, as Elkin et al. (2014) \cite{elkin2014} explained, air4children can provide a way to engage children in problem-solving activities based on Montessori education as well as design activities that allow children to participate in creative explorations, develop fine motor skills, hand-eye coordination, engage in collaborative and teamwork activities.
